A Mountaintop View Requires Minimal Sorting: \break An Instance Optimal Contour Tree Algorithm

### 2014-10-24 paint-contour-tree.tex

\begin{definition} \label{def:tree} The contour tree is the graph on vertex set $\cV$, where
edges are formed as follows. For every contour class that is created at $v_i$ and destroyed $v_j$,
there is an edge $(v_i,v_j)$. (Conventially, edges are directed from higher function value to lower.)
\end{definition}

(It is not immediately obvious that this graph is a tree. But it is equivalent to the Reeb graph
of $f:\MM \rightarrow \RR$, which is known to be a tree.) We denote the contour tree of $\MM$
by $\reeb(\MM,f)$. The corresponding node and edge sets are denoted as $\cV(\cdot)$ and $\cE(\cdot)$.

We use key theorems from~\cite{Carr} (Theorem 6.6) that maps paths in $\cC(\MM)$ and $\MM$.

@@

@@

\pagebreak

>>>>

\begin{definition} \label{def:tree} The contour tree is the graph on vertex set $\cV$, where
edges are formed as follows. For every contour class that is created at $v_i$ and destroyed $v_j$,
there is an edge $(v_i,v_j)$. (Conventionally, edges are directed from higher function value to lower.)
\end{definition}

We denote the contour tree of $\MM$
by $\reeb(\MM) = \reeb(\MM,f)$. The corresponding node and edge sets are denoted as $\cV(\cdot)$ and $\cE(\cdot)$.
%
It is not immediately obvious that this graph is a tree, but the above definition is equivalent to that of the Reeb graph of $f:\MM \rightarrow \RR$ on $\MM$, and this is known to be a tree for PL functions defined over PL manifolds.

\begin{remark}
Note that the contour tree as defined above contains vertices for all critical points, 
which differs slightly from the usual definition which only contains critical points corresponding to a change in the number of contours.  Specifically, if a vertex in the tree we defined has degree $2$ then only the topology of a contour is changing rather than the number of contour.  As such the standard contour tree can be computed from ours by a linear time pass to contract maximal degree 2 vertex paths.

For simplicity we will also make the standard assumption that vertices in the contour 
tree have degree at most $3$, i.e. there are no multi-saddles.
\end{remark}

We use a key theorem from \cite{c-tmi-04} (Theorem 6.6) that maps paths in $\cC(\MM)$ and $\MM$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%end of writup
%stuff below should be deleted
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\remove{

@@

\pagebreak
}
